### 2020-06-01 paper.tex
Add Acronyms to Keywords Section

Very-large-scale integration (VLSI), Standard cell placement, Computer-aided design (CAD), Simulated annealing, Genetic algorithms, Integrated circuits (ICs).

>>>>

Very-large-scale integration (VLSI), Standard cell placement, Computer-aided design (CAD), Simulated annealing (SA), Genetic algorithms (GA), Integrated circuits (ICs).
